Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-30 doc/PRF2022/PRF_main.tex

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$). The streamlines are plotted in the background. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively. The streamlines are plotted in the background.}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.}
\end{figure}
